### 2021-06-11 paper/report.tex

The free parameters are the infection probabilities by contact type, see Supplementary
Material~\ref{subsec:infection_probs}. We estimate these parameters so that  simulated
infections by age predict the corresponding time series in the data \citep[See][for the
    general method]{McFadden1989}. However, the two sets of time series are not comparable
directly because not all cases will be recorded. We thus model recorded cases as
depicted in Figure~\ref{fig:model_for_official_cases}. We take aggregate estimates of
the share of recorded cases and use data on whether the reason for a PCR test were
symptoms of CoViD-19 to get age-specific shares. For example,
\comment[id=HM]{@Janos, please correct if necessary and insert reference} estimate
unknown cases to be twice as high for children as for adults. Confirmation of a positive
rapid test result is another reason for PCR tests, once these become available.

@@

So why is rapid testing so effective? In order to shed more light on this question,
Figure~\ref{fig:2021_scenarios_decomposition_tests} decomposes the difference in the
scenario without rapid tests only (purple line in
Figure~\ref{fig:2021_scenarios_newly_infected}) and the main specification into the three
channels for rapid tests. Tests for pupils have the smallest effect, which is largely
explained by the relatively small number of students (Only 18\% of our population are in
the education sector (pupils, teachers etc.) versus  46\% are workers outside the
education sector) and the fact that schools did not operate at full capacity during our
period of study. Almost 40\% come from tests at the workplace. Despite the fact that rapid tests for private reasons are phased in only late, they make up for more than
half of the total effect.\comment[id=HM]{How many tests are actually performed along each of the three dimensions? Could this be a quantity story rather than the directed testing story I am making up here as wishful thinking?}\comment[id=K]{This is only calculated very deeply inside the model. I'll try to save it.}

The reason lies in the fact that a substantial share of these tests is driven by an
elevated probability to carry the virus, i.e., showing symptoms of CoViD-19 or following
up on a positive test of a household member. The latter is essentially a form of contact
tracing, which has been shown to be very effective \citep{Contreras2021,
Kretzschmar2020}. This is also the reason for why the number of tests performed fall at
the very end of our study period. Falling infection rates mean that there are fewer
events triggering private test demand.
\comment[id=HM]{Positive rates along the three channels might be nice here, if previous
comment is not a quant story}\comment[id=K]{Working on it}
\comment[id=HM]{I think there is a story in here about risk conditional on past exposure
vs. prospective risk in gatherings, but it is too late to work through it. We might just
want to calculate the probabilities.}\comment[id=K]{Yes, we have both in the private
reasons. Retrospective after a case in the household and prospective in anticipation of
participation in a weekly meeting with friends. However, we cannot easily turn these
separately on and off at the moment as they use the same multiplier. We could do,
however, do this in the future.}

Two of the most contentious NPIs concern schools and mandates to work from home. In many
countries, schools switched to remote instruction during the first wave, so did Germany.
After the summer break, they were operating at full capacity with increased hygiene
measures, before being closed again from mid-December on. Some states started opening
them gradually in late February, but usual operaton was not back until the beginning of
June. Figure~\ref{fig:school_scenarios} shows the effects of different policies
regarding school starting at Easter, at which point rapid tests had become widely
available. We estimate the realized scenario to have essentially the same effect as a
situation with closed schools. Under fully opened schools with mandatory tests, total
infections would have been 7\% higher; this number rises to 20\% without tests. These
effect sizes are broadly in line with emprical studies, e.g., \citet{Vlachos2021}
\comment[id=HM]{Need a back-of the envelope calculation} To use another metric, the
effective weekly reproduction number differs by $0.017$ and $0.045$, respectively. In
light of the large negative effects school closures have on children and
parents\comment[id=HM]{need to cite a couple of poor learning outcomes / mental health
papers. There must be well-published ones}---and in particular on those with low
socio-economic status---these results in conjunction with hindsight bias suggest that
opening schools combined with a testing strategy would have been beneficial. In other
situations, and particular when no test strategy is available, trade-offs may well be
different.

>>>>

The free parameters are the infection probabilities by contact type, see Supplementary
Material~\ref{subsec:infection_probs}. We estimate these parameters so that  simulated
infections by age predict the corresponding time series in the data \citep[See][for the
general method]{McFadden1989}. However, the two sets of time series are not comparable
directly because not all cases will be recorded. We thus model recorded cases as depicted
in Figure~\ref{fig:model_for_official_cases}. We take aggregate estimates of the share of
recorded cases and use data on whether the reason for a PCR test were symptoms of
CoViD-19 to get age-specific shares. For example,\comment[id=HM]{@Janos, please correct
if necessary and insert reference} estimate unknown cases to be twice as high for
children as for adults. Confirmation of a positive rapid test result is another reason
for PCR tests, once these become available.

@@

So why is rapid testing so effective? In order to shed more light on this question,
Figure~\ref{fig:2021_scenarios_decomposition_tests} decomposes the difference in the
scenario without rapid tests only (purple line in
Figure~\ref{fig:2021_scenarios_newly_infected}) and the main specification into the three
channels for rapid tests. Tests for pupils have the smallest effect, which is largely
explained by the relatively small number of students (Only 18\% of our population are in
the education sector (pupils, teachers etc.) versus  46\% are workers outside the
education sector) and the fact that schools did not operate at full capacity during our
period of study. Almost 40\% come from tests at the workplace. Despite the fact that rapid tests for private reasons are phased in only late, they make up for more than
half of the total effect.\comment[id=HM]{How many tests are actually performed along each of the three dimensions? Could this be a quantity story rather than the directed testing story I am making up here as wishful thinking?}\comment[id=K]{Working on it.}

The reason lies in the fact that a substantial share of these tests is driven by an
elevated probability to carry the virus, i.e., showing symptoms of CoViD-19 or following
up on a positive test of a household member. The latter is essentially a form of contact
tracing, which has been shown to be very effective \citep{Contreras2021,
Kretzschmar2020}. This is also the reason for why the number of tests performed fall at
the very end of our study period. Falling infection rates mean that there are fewer
events triggering private test demand.\comment[id=HM]{Positive rates along the three
channels might be nice here, if previous comment is not a quant
story}\comment[id=K]{Working on it}\comment[id=HM]{I think there is a story in here about
risk conditional on past exposure vs. prospective risk in gatherings, but it is too late
to work through it. We might just want to calculate the
probabilities.}\comment[id=K]{Yes, we have both in the private reasons. Retrospective
after a case in the household and prospective in anticipation of participation in a
weekly meeting with friends. However, we cannot easily turn these separately on and off
at the moment as they use the same multiplier. We could do, however, do this in the
future.}

Two of the most contentious NPIs concern schools and mandates to work from home. In many
countries, schools switched to remote instruction during the first wave, so did Germany.
After the summer break, they were operating at full capacity with increased hygiene
measures, before being closed again from mid-December on. Some states started opening
them gradually in late February, but usual operation was not back until the beginning of
June. Figure~\ref{fig:school_scenarios} shows the effects of different policies regarding
school starting at Easter, at which point rapid tests had become widely available. We
estimate the realized scenario to have essentially the same effect as a situation with
closed schools. Under fully opened schools with mandatory tests, total infections would
have been 7\% higher; this number rises to 20\% without tests. These effect sizes are
broadly in line with empirical studies, e.g., \citet{Vlachos2021}\comment[id=HM]{Need a
back-of the envelope calculation} To use another metric, the effective weekly
reproduction number differs by $0.017$ and $0.045$, respectively. In light of the large
negative effects school closures have on children and parents\comment[id=HM]{need to cite
a couple of poor learning outcomes / mental health papers. There must be well-published
ones}---and in particular on those with low socio-economic status---these results in
conjunction with hindsight bias suggest that opening schools combined with a testing
strategy would have been beneficial. In other situations, and particular when no test
strategy is available, trade-offs may well be different.
